### 2017-12-24 article.tex
Content filling

\subsubsection{Audit Committee}
JD’s audit committee consists of Louis T. Hsieh, Ming Huang and David Daokui Li. Mr. Hsieh is the chairman of their audit committee.
The audit committee oversees JD’s accounting and financial reporting processes and the audits of the financial statements of our company.
The audit committee is responsible for, among other things:
\begin{itemize}
\item appointing the independent auditors and pre-approving all auditing and non-auditing services permitted to be performed by the independent auditors;
\item reviewing with the independent auditors any audit problems or difficulties and management’s response;
\item discussing the annual audited financial statements with management and the independent auditors;
\item reviewing the adequacy and effectiveness of our accounting and internal control policies and procedures and any steps taken to monitor and control major financial risk exposures;
\item reviewing and approving all proposed related party transactions;
\item meeting separately and periodically with management and the independent auditors;
\item monitoring compliance with our code of business conduct and ethics, including reviewing the adequacy and effectiveness of our procedures to ensure proper compliance.
\end{itemize}

\subsubsection{Nominating and Corporate Governance Committee}
JD’s nominating and corporate governance committee consists of David Daokui Li and Louis T. Hsieh. Mr. Li is the chairperson of their nominating and corporate governance committee. The nominating and corporate governance committee is responsible for, among other things:
\begin{itemize}
\item	selecting and recommending to the board nominees for election by the shareholders or appointment by the board;
\item	reviewing annually with the board the current composition of the board with regards to characteristics such as independence, knowledge, skills, experience and diversity;
\item	making recommendations on the frequency and structure of board meetings and monitoring the functioning of the committees of the board; and
\item	advising the board periodically with regards to significant developments in the law and practice of corporate governance as well as our compliance with applicable laws and regulations, and making recommendations to the board on all matters of corporate governance and on any remedial action to be taken.
\end{itemize}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lcc}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
		    Online direct sales&167,721&237,702\\
			Services and others&13,554&22,420\\
			\qquad\emph{Total}&181,275&260,122\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Revenue (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lcc}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Current income tax expenses&(28,322)&(214,282)\\
			Deferred tax benefits&\underline{42,584}&\underline{34,782}\\
			\qquad\emph{Income tax benefits/(expenses)}&\uuline{14,262}&\uuline{(179,500)}\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Income tax benefits or expenses (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Cash and cash equivalents&17,863,868&19,771,695\\
			Restricted cash&2,114,913&4,391,955\\
			Short-term investments&2,780,482&4,391,955\\
			Investment securities&-&723,449\\
			Accounts receivable, net&8,193,665&17,464,408\\
			Advance to suppliers&927,177&1,423,736\\
			Inventories, net&20,539,543&28,909,438\\
			Loan receivables, net&3,698,488&12,697,915\\
			Other investments&-&10,766,920\\
			Prepayments and other current assets&1,486,441&2,198,906\\
			Amount due from related parties&\underline{863,516}&\underline{1,410,050}\\
			\qquad\emph{Total current assets}&\uuline{58,468,093}&\uuline{106,932,098}\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current assets (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
\begin{center}
	\begin{tabular}{lrr}
		\toprule
		\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
		\midrule
		Cash and cash equivalents&17,863,868&19,771,695\\
		Restricted cash&2,114,913&4,391,955\\
		Short-term investments&2,780,482&4,391,955\\
		Investment securities&-&723,449\\
		Accounts receivable, net&8,193,665&17,464,408\\
		Advance to suppliers&927,177&1,423,736\\
		Inventories, net&20,539,543&28,909,438\\
		Loan receivables, net&3,698,488&12,697,915\\
		Other investments&-&10,766,920\\
		Prepayments and other current assets&1,486,441&2,198,906\\
		Amount due from related parties&\underline{863,516}&\underline{1,410,050}\\
		\qquad\emph{Total current assets}&\uuline{58,468,093}&\uuline{106,932,098}\\
		\bottomrule
	\end{tabular}
\end{center}
	\caption{Current assets (in thousands of RMB \textyen)}\label{table:1}
\end{table}
As we can see, the current assets jumped from \textyen58,468,093,000 to \textyen106,932,098,000.

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Short-term borrowings&3,040,209&8,333,317\\
			Nonrecourse securitization debt&579,843&9,389,213\\
			Accounts payable&29,819,341&4,391,955\\
			Advance from customers&7,173,885&43,988,087\\
			Deferred revenues&983,721&11,632,766\\
			Taxes payable&103,211&1,221,865\\
			Amount due to related parties&104,726&575,848\\
			Accrued expenses and other current liabilities&\underline{7,178,065}&\underline{167,655}\\
			\qquad\emph{Total current liabilities}&\uuline{48,983,001}&\uuline{104,740,235}\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current liabilities (In thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\subsection{Working Capital}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Working capital&9,485,092&2,191,863\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Working capital (In thousands of RMB \textyen)}\label{table:1}
\end{table}

\subsection{Current Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Current ratio&1.194&1.021\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current ratio}\label{table:1}
\end{table}

\subsection{Quick Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Quick ratio&29,819,341&4,391,955\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Quick ratio}\label{table:1}
\end{table}

@@

Inventories, net, consist of the following\footnote{See JD.com, Inc. annual report 2016, Page F-48}:
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Products&20,436,275&28,778,528\\
			Packing materials and others&\underline{103,268}&\underline{130,910}\\
			\qquad\emph{Inventories, net}&\uuline{20,539,543}&\uuline{28,909,438}\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Inventories, net (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Revenue&181,275,425&260,121,645\\
			Cost of goods sold&157,008,329&220,698,727\\
			Gross profit&24,267,096&39,422,918\\
			Gross profit percentage&13.39\%&15.16\%\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Gross profit percentage on sale (in thousands of RMB \textyen\ except for gross profit percentage)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Beginning inventory &12,190,843&20,539,543\\
			Ending inventory  &20,539,543&28,909,438\\
			Average inventory &16,365,193&24,724,490.5\\
			Cost of goods sold &157,008,329&220,698,727\\
			Inventory turnover &9.594&8.826\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Inventory turnover (in thousands of RMB \textyen\ except for inventory turnover)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Accounts receivable &8,465,644&17,880,720\\
			Allowance for doubtful accounts  &\underline{(271,979)}&\underline{(416,312)}\\
			\qquad\emph{Accounts receivable, net} &  \uuline{8,193,665}&\uuline{17,464,408)}\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Accounts receivable (in thousands of RMB \textyen}\label{table:1}
\end{table}

@@

@@

\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}
yu

>>>>

\subsection{Audit Committee}
JD’s audit committee consists of Louis T. Hsieh, Ming Huang and David Daokui Li. Mr. Hsieh is the chairman of their audit committee.
The audit committee oversees JD’s accounting and financial reporting processes and the audits of the financial statements of our company.
The audit committee is responsible for, among other things:
\begin{itemize}
\item appointing the independent auditors and pre-approving all auditing and non-auditing services permitted to be performed by the independent auditors;
\item reviewing with the independent auditors any audit problems or difficulties and management’s response;
\item discussing the annual audited financial statements with management and the independent auditors;
\item reviewing the adequacy and effectiveness of our accounting and internal control policies and procedures and any steps taken to monitor and control major financial risk exposures;
\item reviewing and approving all proposed related party transactions;
\item meeting separately and periodically with management and the independent auditors;
\item monitoring compliance with our code of business conduct and ethics, including reviewing the adequacy and effectiveness of our procedures to ensure proper compliance.
\end{itemize}

\subsection{Nominating and Corporate Governance Committee}
JD’s nominating and corporate governance committee consists of David Daokui Li and Louis T. Hsieh. Mr. Li is the chairperson of their nominating and corporate governance committee. The nominating and corporate governance committee is responsible for, among other things:
\begin{itemize}
\item	selecting and recommending to the board nominees for election by the shareholders or appointment by the board;
\item	reviewing annually with the board the current composition of the board with regards to characteristics such as independence, knowledge, skills, experience and diversity;
\item	making recommendations on the frequency and structure of board meetings and monitoring the functioning of the committees of the board; and
\item	advising the board periodically with regards to significant developments in the law and practice of corporate governance as well as our compliance with applicable laws and regulations, and making recommendations to the board on all matters of corporate governance and on any remedial action to be taken.
\end{itemize}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
		    Online direct sales&167,721&237,702\\
			Services and others&13,554&22,420\\
			\qquad\emph{Total}&181,275&260,122\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Revenue (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrrr}
			\toprule
			&\textbf{2015}&\textbf{2016}&\textbf{Change}\\
			\midrule
			Net revenues&	100&	100&	-\\
			Cost and Expenses& & & \\			
			Cost of revenues&	86.6&	84.8&	(1.8)\\
			Fulfillment&7.7&	8.1	&	0.4\\
			Marketing&	4.3&	4.1	&(0.2)\\
			Technology and content&	1.8&	2.1&	0.3\\
			General and administrative&	1.6	&1.8&	0.2\\
			Impairment of goodwill and intangible assets&	1.5&0&	(1.5)\\
			Other expense&1.5&	0.4	&	(1.1)\\
			Total costs and expenses&	105.0&	101.3&	(3.7)\\
			Loss before taxation&5.0&	1.3	&	(3.7)\\
			Taxation&	(0.007)&	0.008&	0.015\\
			Loss for Year	&5.0&	1.3&	(3.7)\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Common Size Income Statement (in percents)}\label{table:1}
\end{table}

\subsection{Net Loss Before Tax}
The Net Income before tax is as follows:

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lcccc}
			\toprule
			&\textbf{2015}&\textbf{2016}&\textbf{Absolute change}&\textbf{Ralative change}\\

			\midrule
			Net loss before tax&9,132&3,234&(5898)&(64.6\%)\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Net loss before tax (in thousands of RMB \textyen)}\label{table:1}
\end{table}

The loss of the Group decreased by an approximate RMB 5,898,000. The percentage  decrease was 64.6, mainly resulting from decreases in operating expenses especially cost of revenue.

\subsection{Retained Earnings }

The retained earnings are as follows:

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Balance at 1 January&	15,009&	55,560\\
			Statutory reserves&	40,551&	77,378\\
			Balance at 31 December&	55,560&	132,938\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Retained earnings (in thousands of RMB \textyen)}\label{table:1}
\end{table}

The Group’s retained earnings largely increased during year 2015 and 2016. Statutory reserves every year also had a large increase, which indicated full cash flow of the company.

\subsection{Earnings Per Share}
	The Earnings per share is as follows:
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lccc}
			\toprule
			&\textbf{2015}&\textbf{2016}&\textbf{Change}\\
			\midrule
			Basic and diluted earnings per share&(3.33) cents&(1.36) cents&148.12\%\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Earnings per share}\label{table:1}
\end{table}

Earnings per share of the Group was negative due to a negative profit of the company. However, a positive change of it shows that the Group has an improvement in profit.

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lcc}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Current income tax expenses&(28,322)&(214,282)\\
			Deferred tax benefits&\underline{42,584}&\underline{34,782}\\
			\qquad\emph{Income tax benefits/(expenses)}&\uuline{14,262}&\uuline{(179,500)}\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Income tax benefits or expenses (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Cash and cash equivalents&17,863,868&19,771,695\\
			Restricted cash&2,114,913&4,391,955\\
			Short-term investments&2,780,482&4,391,955\\
			Investment securities&-&723,449\\
			Accounts receivable, net&8,193,665&17,464,408\\
			Advance to suppliers&927,177&1,423,736\\
			Inventories, net&20,539,543&28,909,438\\
			Loan receivables, net&3,698,488&12,697,915\\
			Other investments&-&10,766,920\\
			Prepayments and other current assets&1,486,441&2,198,906\\
			Amount due from related parties&\underline{863,516}&\underline{1,410,050}\\
			\qquad\emph{Total current assets}&\uuline{58,468,093}&\uuline{106,932,098}\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current assets (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
\begin{center}
	\begin{tabular}{lrr}
		\toprule
		&\textbf{2015}&\textbf{2016}\\
		\midrule
		Cash and cash equivalents&17,863,868&19,771,695\\
		Restricted cash&2,114,913&4,391,955\\
		Short-term investments&2,780,482&4,391,955\\
		Investment securities&-&723,449\\
		Accounts receivable, net&8,193,665&17,464,408\\
		Advance to suppliers&927,177&1,423,736\\
		Inventories, net&20,539,543&28,909,438\\
		Loan receivables, net&3,698,488&12,697,915\\
		Other investments&-&10,766,920\\
		Prepayments and other current assets&1,486,441&2,198,906\\
		Amount due from related parties&\underline{863,516}&\underline{1,410,050}\\
		\qquad\emph{Total current assets}&\uuline{58,468,093}&\uuline{106,932,098}\\
		\bottomrule
	\end{tabular}
\end{center}
	\caption{Current assets (in thousands of RMB \textyen)}\label{table:1}
\end{table}
As we can see, the current assets jumped from \textyen58,468,093,000 to \textyen106,932,098,000.

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Short-term borrowings&3,040,209&8,333,317\\
			Nonrecourse securitization debt&579,843&9,389,213\\
			Accounts payable&29,819,341&4,391,955\\
			Advance from customers&7,173,885&43,988,087\\
			Deferred revenues&983,721&11,632,766\\
			Taxes payable&103,211&1,221,865\\
			Amount due to related parties&104,726&575,848\\
			Accrued expenses and other current liabilities&\underline{7,178,065}&\underline{167,655}\\
			\qquad\emph{Total current liabilities}&\uuline{48,983,001}&\uuline{104,740,235}\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current liabilities (In thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\subsection{Working Capital}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Working capital&9,485,092&2,191,863\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Working capital (In thousands of RMB \textyen)}\label{table:1}
\end{table}

\subsection{Current Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Current ratio&1.194&1.021\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current ratio}\label{table:1}
\end{table}

\subsection{Quick Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Quick ratio&29,819,341&4,391,955\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Quick ratio}\label{table:1}
\end{table}

@@

Inventories, net, consist of the following\footnote{See JD.com, Inc. annual report 2016, Page F-48}:
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Products&20,436,275&28,778,528\\
			Packing materials and others&\underline{103,268}&\underline{130,910}\\
			\qquad\emph{Inventories, net}&\uuline{20,539,543}&\uuline{28,909,438}\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Inventories, net (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Revenue&181,275,425&260,121,645\\
			Cost of goods sold&157,008,329&220,698,727\\
			Gross profit&24,267,096&39,422,918\\
			Gross profit percentage&13.39\%&15.16\%\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Gross profit percentage on sale (in thousands of RMB \textyen\ except for gross profit percentage)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Beginning inventory &12,190,843&20,539,543\\
			Ending inventory  &20,539,543&28,909,438\\
			Average inventory &16,365,193&24,724,490.5\\
			Cost of goods sold &157,008,329&220,698,727\\
			Inventory turnover &9.594&8.826\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Inventory turnover (in thousands of RMB \textyen\ except for inventory turnover)}\label{table:1}
\end{table}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Accounts receivable &8,465,644&17,880,720\\
			Allowance for doubtful accounts  &\underline{(271,979)}&\underline{(416,312)}\\
			\qquad\emph{Accounts receivable, net} &  \uuline{8,193,665}&\uuline{17,464,408)}\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Accounts receivable (in thousands of RMB \textyen}\label{table:1}
\end{table}

@@

\subsection{Depreciation}

Property, equipment and software are stated at cost less accumulated depreciation and impairment. Property, equipment and software are depreciated at rates sufficient to write off their costs less impairment and residual value, if any, over the estimated useful lives on a straight-line basis. Repairs and maintenance costs are charged to expenses as incurred, whereas the costs of renewals and betterment that extend the useful lives of property, equipment and software are capitalized as additions to the related assets. The estimated useful lives are as follows:

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{l|p{5cm}}
			\hline
			\textbf{\large{Category}}&\textbf{\large{Estimated Useful Lives}}\\
			\hline
			\rowcolor[gray]{.95}
			Category Estimated useful lives Electronic equipment &	3 years\\
			Office equipment &	5 years\\
			\rowcolor[gray]{.95}
			Vehicles&	5 years\\
			Logistic and warehouse equipment &	5 years\\
			\rowcolor[gray]{.95}
			Leasehold improvement&	Over the shorter of the expected life of leasehold improvements or the lease term\\			
			Software&	3-5 years\\
			\rowcolor[gray]{.95}
			Building &	40 years\\
			Building improvement &	5-10 years\\
		\end{tabular}
	\end{center}
	\caption{The estimated useful lives}\label{table:1}
\end{table}

\subsection{Depreciation Expense}

In total, Depreciation expenses were RMB1,123,076 and RMB1,944,606 for the years ended December 31, 2015 and 2016, respectively.

\subsection{Impairment}
Short-term investments: No impairment charges were recorded for the years ended December 31, 2014, 2015 and 2016, respectively.

Long-lived assets are evaluated for impairment whenever events or changes in circumstances (such as a significant adverse change to market conditions that will impact the future use of the assets) indicate that the carrying value of an asset may not be fully recoverable or that the useful life is shorter than the Group had originally estimated. When these events occur, the Group evaluates the impairment for the long-lived assets by comparing the carrying value of the assets to an estimate of future undiscounted cash flows expected to be generated from the use of the assets and their eventual disposition. If the sum of the expected future undiscounted cash flows is less than the carrying value of the assets, the Group recognizes an impairment loss based on the excess of the carrying value of the assets over the fair value of the assets.

Goodwill: The Group recorded an impairment charge of nil, RMB2,593,420 and nil for the years ended December 31, 2014, 2015 and 2016, respectively.

Intangible assets: The Group recorded an impairment charge of nil, RMB156,709 and nil for the years ended December 31, 2014, 2015 and 2016.

Investment: JD performs impairment assessment of its investments under the cost method and equity method whenever events or changes in circumstances indicate that the carrying value of the investment may not be fully recoverable. Impairment charges in connection with the cost method investments of nil, RMB285,051 and RMB436,621 were recorded in others, net for the years ended December 31, 2014, 2015 and 2016, respectively. Impairment charges in connection with the equity method investments of nil, RMB2,585,641 and RMB1,416,801 were recorded in share of results of equity investees for the years ended December 31, 2014, 2015 and 2016, respectively.

\subsection{Revaluation}
The company did not revalue any of its long-term assets.

\section{Long-Term Liabilities and Contingent Liabilities}

\subsection{Long-Term Liabilities}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Deferred revenues& 	2,556,345&	2,156,835\\
			Nonrecourse securitization debt  &	2,753,699&	4,077,627\\
			Unsecured senior notes  &	-&	6,831,012\\
			Deferred tax liabilities &	1,228&	907,356\\
			Other non-current liabilities &	-&	440,670\\
			\qquad\emph{Total non-current liabilities}&	5,311,272&	14,413,500\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Non-current liabilities (in thousands of RMB \textyen)}\label{table:1}
\end{table}

Deferred revenues include amounts in relation to traffic support, marketing and promotion services to be provided to related parties of 2,515,603 and RMB2,127,900 as of December 31, 2015 and 2016. Other non-current liabilities are related to non-compete obligation to related party of nil and RMB 440,670 as of December 31, 2015 and 2016.

The Group’s non-current liabilities increase by 9,102,228,000 in FY 2016, as compared with the previous financial year. And all the items increase expect for deferred revenues.

\subsection{Security of Long-Term Liabilities}
The Group’s long-term debt obligations include unsecured senior notes and nonrecourse securitization debt which consists of asset-backed debt securities issued in connection with securitization of certain financial assets. The expected repayment amount of the nonrecourse securitization debt is approximately RMB9,389,213 and RMB4,077,627 for the years ended December 31, 2017 and 2018, respectively. The unsecured senior notes contain covenants including, among others, limitation on liens, consolidation, merger and sale all or substantially all of the Company’s assets. The proceeds from issuance of the unsecured senior notes were used for general corporate purposes. As of December 31, 2016, the principal of the unsecured senior notes of RMB3,468,500 and RMB3,468,500 will be due in 2021 and 2026, respectively.

\subsection{Total Assets Financed by Long-Term Borrowings}

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{p{8.3cm}rr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Total current assets&	58,468,093&	106,932,098\\
			Total non-current assets &	26,547,046&	53,441,420\\
			Total assets &	85,015,139&	160,373,518\\
			Total non-current liabilities excluding deferred tax &	5,310,044&	13,506,144\\
			Proportion of the total assets of the company financed by long-term borrowings	&6.2\%&	8.4\%\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{total assets financed by long-term borrowings (in thousands of RMB \textyen)}\label{table:1}
\end{table}

From the above table, we can see that the percentage increase by about 2\%. This means that JD is just slightly more reliant on external parties to finance its total assets.

\subsection{Long-term Assets Finance Options}
The use of internally generated funds as a finance option does not incur any future interest costs. Moreover, investment projects can be undertaken without involving either the shareholders or any outsiders. However, it is evident that JD has negative retained earnings, or accumulated losses of \textyen21,860,345,000. Hence, utilizing internally generated funding for the purchase of long-term assets is a less feasible option, as it will hamper the recovery of the company’s accumulated losses.

Long-term bank loans are a viable option. The loans are secured by mortgage of long-term assets. Considering the fact that JD’s Proportion of the total assets of the company financed by long-term borrowings is low and JD will probably not require substantially large sums for expansion of property, plant and equipment, it would be a helpful source of financing.

As for funds from shareholders’ contributions, issuing shares creates no liabilities and in addition, there is no demand for repayment. Issuing new ordinary shares to the public is will generate the required funds for the company. This would, however, dilute the holdings of the shareholders and may cause disapproval among shareholders. Issuance of new shares also implies that a larger amount of dividend needs to be paid in future, owing to the increase in outstanding shares. On the other hand, issuance of preference shares is advantageous for JD because dividends do not have to be paid in a year in which the company’s performance is poor.

\subsection{Contingent Items}
The company did not have any contingent items.

\section{Statement of Cash Flows}
\subsection{Cash Position}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Effect of exchange rate changes on cash and cash equivalents &	343,147&	709,916\\
			Net increase in cash and cash equivalents &949,217&	1,907,827\\
			Cash and cash equivalents at beginning of year 	&16,914,651&	17,863,868\\
			Cash and cash equivalents at end of year&	17,863,868	&19,771,695\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Cash position (in thousands of RMB \textyen)}\label{table:1}
\end{table}

JD experienced a stable increase in cash and cash equivalents in FY 2015 and FY 2016, and cash and cash equivalents at financial year-end of 2016 showed an increase of \textyen1,907,827,000, twice times more than that of 2015.

\subsection{Operating, Investing and Financing}

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Net cash provided by operating activities&	1,696,322&	8,767,017\\
			Net cash used in investing activities&	(5,790,525)&	(48,268,577)\\
			Net cash provided by financing activities&	(4,700,273)	&(40,699,471)\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Net cash flows (in thousands of RMB \textyen)}\label{table:1}
\end{table}

Net cash provided by operating activities increased by \textyen7,070,695,000, a 417\% increase.  
The net cash used in investing activities increases by \textyen42,478,052,000 from FY 2015 to FY 2016. Therefore, the net cash used in investing activities increases by nearly 734\% from FY 2006 to FY 2007
The net cash provided in financing activities increased by \textyen35,999,198,000 from FY 2015 to FY 2016. Thus, this shows a 766\% increase in net cash used in financing activities.
These changes are dramatic. From Consolidated Statements of Cash Flows, we can find the main reasons for each change:
The increase of net cash provided by operating activities is mainly due to the decrease of net loss. It indicates better performance of JD in operating activities.
The increase of the net cash used in investing activities is mainly caused by purchasing of other investments and paying for loan originations. It indicates that JD is increasing investment. And it also indicates the effect of JD Finance has changed from supporting the overall JD platform to an independently operated and self-funded business.
The increase of net cash provided by financing activities is mainly because of Proceeds from sales of financial products and Capital injection from non-controlling interest shareholders compared with the previous year. It also indicates part of the effect of JD Finance has changed from supporting the overall JD platform to an independently operated and self-funded business.

\subsection{Preparation of Operating Cash Flows}
JD used the indirect method in the preparation of operation cash flow.

\subsection{Statement of Cash Flow}
The Statement of Cash Flows helps JD to predict future cash flows, evaluate management decisions, and to predict ability to pay its debts and dividends. The balance sheet and the income sheet is unable to show why cash increased or decreased.

First, the Statement of Cash Flows adds information to show why cash increased or decreased. Cash receipts show exactly where cash came from, and the cash payments show exactly where cash was spent.

Then, the statement of cash flow also helps to predict future cash flows, as past cash receipts and payments help predict future cash flows through trends and patterns
Furthermore, the Statement of Cash Flows helps to make predictions on JD’s ability to pay its debts and dividends.

\subsection{Positive Cash Flow from Operations Despite Recording Losses}
JD is such an example that records a loss and yet has a positive cash flow from operations. The Statement of Cash Flows is prepared under cash basis accounting, while the Balance Sheet and the Income Statement are prepared under the accrual basis of accounting. The differences between these two kinds of accountings makes it possible for a company to record a loss and yet have a positive cash flow from operations. Other items’ sum is positive enough.

Taking JD itself as an example, accounts payable, advance from customers, depreciation expenses and impairment losses are the main cause.

As we can see, in the Statement of Cash Flows, though the net loss is pretty high, but accrued expenses, accounts payable, advance from customers, depreciation expenses and impairment losses are higher, especially accounts payable. As a result, cash Flows from Operations are still positive.

\section{Market Prices of Shares}
According to NASDAQ Exchange Stock Chart, at balance sheet date 30 Dec 2016, the market price of JD was \$25.44.

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{p{11cm}r}
			\toprule
			&\textbf{Dec.31, 2016}\\
			\midrule
			Total shareholders’ equity (in thousands of US dollars)&	4,920,475\\
			No. of Ordinary Shares Issued (in thousands of US dollars) &	2,938,709\\
			Book Value per Share (in US dollars) &	1.67\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Market prices}\label{table:1}
\end{table}

@@

\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}
